\begingroup
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\sloppy
\begin{thebibliography}{99}

\bibitem{angular-doc}
Angular Team, ``Angular Documentation,'' Angular, 2026. [Online]. Available: \url{https://angular.dev/}. [Accessed: May 21, 2026].

\bibitem{spring-boot-doc}
VMware, ``Spring Boot Reference Documentation,'' Spring, 2026. [Online]. Available: \url{https://docs.spring.io/spring-boot/index.html}. [Accessed: May 21, 2026].

\bibitem{tailwind-doc}
Tailwind Labs, ``Tailwind CSS Documentation,'' Tailwind CSS, 2026. [Online]. Available: \url{https://tailwindcss.com/docs}. [Accessed: May 21, 2026].

\bibitem{typescript-doc}
Microsoft, ``TypeScript Documentation,'' TypeScript, 2026. [Online]. Available: \url{https://www.typescriptlang.org/docs/}. [Accessed: May 21, 2026].

\bibitem{docker-doc}
Docker Inc., ``Docker Documentation,'' Docker Docs, 2026. [Online]. Available: \url{https://docs.docker.com/}. [Accessed: May 21, 2026].

\bibitem{keycloak-doc}
Keycloak Contributors, ``Keycloak Documentation,'' Keycloak, 2026. [Online]. Available: \url{https://www.keycloak.org/documentation}. [Accessed: May 21, 2026].

\bibitem{opa-doc}
Open Policy Agent Contributors, ``Open Policy Agent Documentation,'' OPA, 2026. [Online]. Available: \url{https://www.openpolicyagent.org/docs/latest/}. [Accessed: May 21, 2026].

\bibitem{mongodb-doc}
MongoDB Inc., ``MongoDB Documentation,'' MongoDB, 2026. [Online]. Available: \url{https://www.mongodb.com/docs/}. [Accessed: May 21, 2026].

\bibitem{postgresql-doc}
The PostgreSQL Global Development Group, ``PostgreSQL Documentation,'' PostgreSQL, 2026. [Online]. Available: \url{https://www.postgresql.org/docs/}. [Accessed: May 21, 2026].

\bibitem{minio-doc}
MinIO, Inc., ``MinIO Documentation,'' MinIO, 2026. [Online]. Available: \url{https://min.io/docs/minio/container/index.html}. [Accessed: May 21, 2026].

\bibitem{kafka-doc}
The Apache Software Foundation, ``Apache Kafka Documentation,'' Apache Kafka, 2026. [Online]. Available: \url{https://kafka.apache.org/documentation/}. [Accessed: May 21, 2026].

\bibitem{onlyoffice-doc}
Ascensio System SIA, ``ONLYOFFICE Docs API,'' ONLYOFFICE, 2026. [Online]. Available: \url{https://api.onlyoffice.com/docs/docs-api/}. [Accessed: May 21, 2026].

\bibitem{plantuml-doc}
PlantUML, ``PlantUML Documentation,'' PlantUML, 2026. [Online]. Available: \url{https://plantuml.com/}. [Accessed: May 21, 2026].

\bibitem{diagramsnet-doc}
JGraph Ltd., ``diagrams.net,'' diagrams.net, 2026. [Online]. Available: \url{https://www.diagrams.net/}. [Accessed: May 21, 2026].

\bibitem{git-doc}
Git Project, ``Git Documentation,'' Git SCM, 2026. [Online]. Available: \url{https://git-scm.com/docs}. [Accessed: May 21, 2026].

\bibitem{uml-spec}
Object Management Group, ``OMG Unified Modeling Language (OMG UML), Version 2.5.1,'' Dec. 2017. [Online]. Available: \url{https://www.omg.org/spec/UML/2.5.1}. [Accessed: May 21, 2026].

\bibitem{soa-erl}
T. Erl, \textit{Service-Oriented Architecture: Concepts, Technology, and Design}. Upper Saddle River, NJ, USA: Prentice Hall PTR, 2005.

\bibitem{microservices-newman}
S. Newman, \textit{Building Microservices: Designing Fine-Grained Systems}. Sebastopol, CA, USA: O'Reilly Media, 2015.

\bibitem{clean-arch}
R. C. Martin, \textit{Clean Architecture: A Craftsman's Guide to Software Structure and Design}. Boston, MA, USA: Pearson, 2017.

\bibitem{rbac-sandhu}
R. Sandhu, E. J. Coyne, H. L. Feinstein, and C. E. Youman, ``Role-Based Access Control Models,'' \textit{Computer}, vol. 29, no. 2, pp. 38--47, Feb. 1996.

\bibitem{oauth2-rfc6749}
D. Hardt, Ed., ``The OAuth 2.0 Authorization Framework,'' RFC 6749, Oct. 2012. [Online]. Available: \url{https://www.rfc-editor.org/rfc/rfc6749}. [Accessed: May 21, 2026].

\bibitem{oidc-core}
N. Sakimura \textit{et al.}, ``OpenID Connect Core 1.0 incorporating errata set 1,'' OpenID Foundation, Nov. 2014. [Online]. Available: \url{https://openid.net/specs/openid-connect-core-1_0.html}. [Accessed: May 21, 2026].

\bibitem{eda-fowler}
M. Fowler, ``What do you mean by Event-Driven?,'' martinfowler.com, Feb. 2017. [Online]. Available: \url{https://martinfowler.com/articles/201701-event-driven.html}. [Accessed: May 21, 2026].

\end{thebibliography}
\endgroup
