\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
\markboth{General Conclusion}{General Conclusion}

This internship project resulted in the design and implementation of Football
OS, a unified digital platform for football club operations. The objective was
to reduce fragmentation caused by separate tools and to provide a secured
workspace for document management, event planning, player profile consultation,
notifications, and search. The final solution was built as a
microservices-oriented backend organized in a monorepo, structured around the
API Gateway, the Governance Service, the Workspace Service, and the Shared SDK.
\vspace{0.15cm}

The implemented platform covers the main functional scope defined in this
report. Authentication and protected routing are integrated end to end,
governance roles and policy decisions control sensitive actions, and document
workflows are handled through version-aware metadata separated from object
storage. Calendar and event operations support planning and coordinated
follow-up, while player profile access is filtered by permissions. In addition,
notification mechanisms improve operational visibility, and OnlyOffice
integration enables authorized users to consult and edit documents online in a
controlled workflow.
\vspace{0.15cm}

Beyond feature delivery, the project provided important engineering lessons.
The distributed nature of the solution required careful handling of service
communication, identity propagation, policy debugging, document versioning, and
coordination between MongoDB, PostgreSQL, MinIO, Keycloak, OPA, and the
Gateway. The architectural choice of separating edge access, governance
responsibilities, workspace operations, and shared SDK abstractions improved
modularity, but it also introduced integration complexity that had to be
managed during implementation and validation.
\vspace{0.15cm}

The validation phase confirmed that the prototype behaves coherently in the
local Docker-based environment. Functional tests, security checks, and local
latency observations showed that the main workflows operate as expected for
development use. However, the platform still requires broader automated
testing, stronger end-to-end validation, production monitoring, load
evaluation, and further UI/UX refinement before production-scale adoption.
Overall, Football OS provides a solid and extensible foundation for future
football-specific workflows and demonstrates how a governed digital workspace
can improve coordination, traceability, and controlled collaboration inside
football organizations.
